Untitled

### 2023-04-13 Main_Figures/Other_figs/Analysis_1_Separated.Rmd
edits for final sub

#LOAD LIBRARIES 
library(phytools)
library(ape) #for phylogenetic distance
library(dplyr) #data processing
library(rtrees) #for phylogenetic distancelibrary(MASS)
library(reshape2)
library(viridis) #COLOUR GGPLOT
library(MASS)
library(ggplot2)
library(broman) #crayon colours
library(tidyverse)
library(patchwork) #panel of plots
library(brms)
library(cmdstanr)

@@

combined <- p1 + p2 + p3 + pp1 + pp2 + pp3 & theme(legend.position = "right")
combined + plot_layout(guides = "collect",ncol = 3)

>>>>

#LOAD LIBRARIES 
library(phytools)
library(ape) #for phylogenetic distance
library(dplyr) #data processing
library(rtrees) #for phylogenetic distancelibrary(MASS)
library(reshape2)
library(viridis) #COLOUR GGPLOT
library(MASS)
library(ggplot2)
library(broman) #crayon colours
library(tidyverse)
library(patchwork) #panel of plots
library(brms)

@@

combined <- pp1 + pp2 + pp3 + p1 + p2 + p3 & theme(legend.position = "bottom")
combined + plot_layout(guides = "collect",ncol = 3)

### 2023-04-13 Main_Figures/Other_figs/Traits_Table.Rmd
edits for final sub

n_of_records <- subset(missing.values, isna=="FALSE")
Trait <- c("Plant height (m)", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovules per flower",
           "Flowers per plant", "Nectar ($\\mu$l)", "Nectar (mg)", "Nectar concentration ($\\%$)", "Pollen grains per flower", "Autonomous selfing (fruit set)")

@@

kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("l","l","l")) %>%
  kable_styling(full_width = F,font_size = 10) %>%
  add_header_above(c("Quantitative traits" = 1,"Qualitative traits" = 2),bold=T)   %>% row_spec(0, bold=T)

>>>>

n_of_records <- subset(missing.values, isna=="FALSE")
Trait <- c("Plant height (m)", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovules per flower",
           "Flowers per plant", "Nectar ($\\mu$l)", "Nectar (mg)", "Nectar concentration ($\\%$)", "Pollen grains per flower", "Autonomous selfing")

@@

kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("l","l","l")) %>%
  kable_styling(full_width = F,font_size = 10) %>%
  add_header_above(c("Quantitative traits" = 1,"Qualitative traits" = 2),bold=T)   %>% row_spec(0:12, bold=T) %>% save_kable(file = "table_1.png",density = 700)
